A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-14 Paper.tex
with new image

		\begin{figure}
			\centering
			\includegraphics[height=40mm,width=90mm]{Trilateration_methods.JPG}
			\caption{The red arrow represents the robot.The 'X' represents the origin of the robot. The blue line shows the traversed path.The star represents the landmark. }
		\end{figure}

@@

In /cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM. It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small. This approach is validated for both simulated and real data sets. This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.

>>>>

		\begin{figure}
			\centering
			\includegraphics[height=30mm,width=90mm]{Trilateration_methods.JPG}
			\caption{The red arrow represents the robot.The 'X' represents the origin of the robot. The blue line shows the traversed path.The star represents the landmark. }
		\end{figure}

@@

In \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM. It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small. This approach is validated for both simulated and real data sets. This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.
